---
title: "Practice Testing Big Data Analyses"
output:
  html_document:
    number_sections: yes
    toc: yes
  pdf_document:
    toc: yes
---
```{r Setup, include=FALSE}
rm(list=ls())
library(readr)
library(lmerTest)
library(plyr)
library(psych)
library(sjPlot)
library(car)
library(gridExtra)
library(MuMIn)
library(data.table)
library(sciplot)
library(lattice)
library(dplyr)
library(ggplot2)
library(optimx)
library(sjstats)
library(tidyverse)
library(lubridate)
library(ggpubr)
```

# Import datasets and merge all datasets
```{r}
#import
SumData_ds863 <- read_csv("measures/SumData_ds863_rev.csv")

SumData_ds2033 <- read_csv("measures/SumData_ds2033_rev.csv")

SumData_ds490 <- read_csv("/measures/SumData_ds490_rev.csv")

#merge
dbs <-  rbind(SumData_ds863,SumData_ds2033,SumData_ds490)
dbs <- dbs %>% distinct(ds_anon_user_id, module, .keep_all = TRUE)
as.data.table(dbs)


```

# Add variables not in dataset yet
```{r}
dbs$time_perPage <-  dbs$TimeReadTrimmed/dbs$NRead_trimmed
dbs$time_perDo <-  dbs$TimeAction/dbs$NAction
dbs$time_perPage <-  ifelse(is.na(dbs$time_perPage),0,dbs$time_perPage)
dbs$time_perDo <-   ifelse(is.na(dbs$time_perDo),0,dbs$time_perDo)

dbs$time_perPage <-  ifelse(is.infinite(dbs$time_perPage),0,dbs$time_perPage)
dbs$time_perDo <-   ifelse(is.infinite(dbs$time_perDo),0,dbs$time_perDo)

dbs$correctness_alltries <- ifelse(is.na(dbs$correctness_alltries),0,dbs$correctness_alltries)      
dbs$correctness_firsttry <- ifelse(is.na(dbs$correctness_firsttry),0,dbs$correctness_alltries)            
dbs$meanAttempts <- ifelse(is.na(dbs$meanAttempts),0,dbs$correctness_alltries)

dbs$repeated_activities <- dbs$NAction - dbs$NAction_unique
dbs$repeated_pages <- dbs$NRead_trimmed - dbs$NRead_trimmed_unique
dbs$alternation <- dbs$CountActionToPage + dbs$CountPageToAction

dbs$percentActivities <- ifelse(is.na(dbs$percentActivities),0,dbs$percentActivities)
dbs$percentPages <- ifelse(is.na(dbs$percentPages),0,dbs$percentPages)

dbs$percentActivities <- ifelse(dbs$percentActivities=="Inf",0,dbs$percentActivities)
dbs$percentPages <- ifelse(dbs$percentPages=="Inf",0,dbs$percentPages)

dbs$activity_group <- ifelse(dbs$NAction>0,"2_Activities","1_No Activities")
dbs$read_group <- ifelse(dbs$NRead_trimmed>0,"2_Read","1_No Read")

```

# Descriptives for the dataset
```{r}
describe(dbs)
describeBy(x = dbs,group = dbs$domain)
describeBy(x = dbs,group = dbs$dataset)
descriptivesPsych <- describe(dbs[dbs$domain=="psych",])
descriptivesComputing <- describe(dbs[dbs$domain=="c@cm",])

write.csv(descriptivesPsych,file = "DescriptivesPsych.csv",row.names = TRUE)
write.csv(descriptivesComputing,file = "DescriptivesComputing.csv",row.names = TRUE)
```

# Normalize things
```{r}
dbs <- ddply(.data = dbs,.variables = .(dataset),.fun = mutate,
             zNRead = scale(NRead),
             zNread_unique=scale(NRead_unique),
             zNRead_trimmed=scale(NRead_trimmed),
             zNRead_trimmed_unique=scale(NRead_trimmed_unique),
             zNAction=scale(NAction),zNAction_unique=scale(NAction_unique),
             logTimeRead = log(TimeRead),
             logTimeReadTrimmed=log(TimeReadTrimmed),
             logTimeAction=log(TimeAction),
             logTimeActionToPage=log(TimeActionToPage),
             logTimePageToAction=log(TimePageToAction),
             zCountActionToPage=scale(CountActionToPage),
             zCountPageToAction=scale(CountPageToAction),
             zreading_rate=scale(reading_rate),
             zpercentActivities=scale(percentActivities),
             zpercentPages=scale(percentPages),
             logretention_interval=log(retention_interval),
             zcorrectness_alltries=scale(correctness_alltries),
             zcorrectness_firsttry=scale(correctness_firsttry),
             zmeanAttempts=scale(meanAttempts),
             zpretestGrade=scale(pretestGrade),
             zquizGrade=scale(quizGrade),
             zexamGrade=scale(examGrade),
             logtime_perPage=log(time_perPage),
             logtime_perDo=log(time_perDo),
             zrepeated_activities=scale(repeated_activities),
             zrepeated_pages=scale(repeated_pages),
             zalternation=scale(alternation),
             .progress = "text")

is.na(dbs) <- do.call(cbind,lapply(dbs, is.infinite))
```

# Check variability for each domain/dataset
```{r}
var_db_psych <- ddply(.data = dbs[dbs$dataset=="ds863",],.variables = .(ds_anon_user_id),.fun = summarize,cv_do=sd(NAction,na.rm = T)/mean(NAction,na.rm = T),cv_read=sd(NRead_trimmed,na.rm = T)/mean(NRead_trimmed,na.rm = T),sd_do=sd(NAction,na.rm = T),sd_read=sd(NRead_trimmed,na.rm = T))
var_db_psych
mean(var_db_psych$sd_do,na.rm=T)
min(var_db_psych$sd_do,na.rm=T)
max(var_db_psych$sd_do,na.rm=T)
mean(var_db_psych$sd_read,na.rm=T)

var_module_db_psych <- ddply(.data = dbs[dbs$dataset=="ds863",],.variables = .(module),.fun = summarize,cv_do=sd(NAction)/mean(NAction),cv_read=sd(NRead_trimmed)/mean(NRead_trimmed),sd_do=sd(NAction),sd_read=sd(NRead_trimmed))
var_module_db_psych
mean(var_module_db_psych$sd_do,na.rm=T)
min(var_module_db_psych$sd_do)
max(var_module_db_psych$sd_do)
mean(var_module_db_psych$sd_read)

var_db_ccm <- ddply(.data = dbs[!dbs$dataset=="ds863",],.variables = .(ds_anon_user_id),.fun = summarize,cv_do=sd(NAction,na.rm = T)/mean(NAction,na.rm = T),cv_read=sd(NRead_trimmed,na.rm = T)/mean(NRead_trimmed,na.rm = T),sd_do=sd(NAction,na.rm = T),sd_read=sd(NRead_trimmed,na.rm = T))
var_db_ccm

var_module_db_ccm <- ddply(.data = dbs[!dbs$dataset=="ds863",],.variables = .(module),.fun = summarize,cv_do=sd(NAction)/mean(NAction),cv_read=sd(NRead_trimmed)/mean(NRead_trimmed),sd_do=sd(NAction),sd_read=sd(NRead_trimmed))
var_module_db_ccm

```

# HISTOGRAMS
```{r}
p <- ddply(.data = dbs,.variables = .(ds_anon_user_id,dataset),.fun = mutate,byModule=ifelse(quizGrade>mean(quizGrade),"Above","Below"))

p <- ddply(.data = p,.variables = .(module,dataset),.fun = mutate,byStudent=ifelse(quizGrade>mean(quizGrade),"Above","Below"))

ggplot(p, aes(x=percentActivities,color=byModule)) + geom_histogram(position="identity") +  facet_wrap(. ~ domain,nrow=1) +  labs(title = "Analyses by Workspace",y="N Students",x="% Activities") + geom_histogram(fill="white")

ggplot(p, aes(x=percentPages,color=byModule)) + geom_histogram(position="identity") +  facet_wrap(. ~ domain,nrow=1) +  labs(title = "Analyses by Workspace",y="N Students",x="% Pages") + geom_histogram(fill="white")

ggplot(p, aes(x=percentActivities,color=byStudent)) + geom_histogram(position="identity") +  facet_wrap(. ~ domain,nrow=1) +  labs(title = "Analyses by Workspace",y="N Students",x="% Activities") + geom_histogram(fill="white")

ggplot(p, aes(x=percentPages,color=byStudent)) + geom_histogram(position="identity") +  facet_wrap(. ~ domain,nrow=1) +  labs(title = "Analyses by Workspace",y="N Students",x="% Pages") + geom_histogram(fill="white")

ggplot(data = dbs, aes(x=percentPages*100)) + geom_histogram(position="identity") +  facet_wrap(. ~ domain,nrow=1) +  labs(title = "Pages Viewed",y="# Students-Module pairs",x="% Pages") + geom_histogram(fill="grey")

ggplot(data = dbs, aes(x=percentActivities*100)) + geom_histogram(position="identity") +  facet_wrap(. ~ domain,nrow=1) +  labs(title = "Activities Completed",y="# Students-Module pairs",x="% Activities") + geom_histogram(fill="grey")

ggplot(data = dbs, aes(x=quizGrade*100)) + geom_histogram(position="identity") +  facet_wrap(. ~ domain,nrow=1) +  labs(title = "Quiz Grades",y="# Students-Module pairs",x="Quiz Grade") + geom_histogram(fill="grey")

ggplot(data = dbs, aes(x=pretestGrade*100)) + geom_histogram(position="identity") +  facet_wrap(. ~ domain,nrow=1) +  labs(title = "Pretest Scores",y="# Students-Module pairs",x="Pretest Score") + geom_histogram(fill="grey")

ggplot(data = dbs, aes(x=log(retention_interval))) + geom_histogram(position="identity") +  facet_wrap(. ~ domain,nrow=1) +  labs(title = "Retention Interval",y="# Students-Module pairs",x="Log(Retention Interval)") + geom_histogram(fill="grey")

p <- as.data.table(dbs)[,.(nquizzes=length(module)),by=.(ds_anon_user_id,domain)]
ggplot(data = p, aes(x=nquizzes)) + geom_histogram(position="identity") +  facet_wrap(. ~ domain,nrow=1) +  labs(title = "Number of Modules Completed",y="# Students",x="Quiz Grade") + geom_histogram(fill="grey")

ggarrange(problems, time, common.legend = TRUE, ncol = 1, nrow = 2, legend = "bottom")

```

## Psych
```{r}
psych_pages <- ggplot(data = dbs[dbs$domain=="psych",], aes(x=percentPages*100)) + geom_histogram(position="identity") +  labs(title = "b Pages Viewed",y="# Students-Module pairs",x="% Pages") + geom_histogram(fill="grey")

psych_act <- ggplot(data = dbs[dbs$domain=="psych",], aes(x=percentActivities*100)) + geom_histogram(position="identity") + labs(title = "a Activities Completed",y="# Students-Module pairs",x="% Activities") + geom_histogram(fill="grey")

psych_rep_pages <- ggplot(data = dbs[dbs$domain=="psych",], aes(x=repeated_pages)) + geom_histogram(position="identity") +  labs(title = "d Repeated Pages",y="# Students-Module pairs",x="# Repeated Pages") + geom_histogram(fill="grey")

psych_rep_act <- ggplot(data = dbs[dbs$domain=="psych",], aes(x=repeated_activities)) + geom_histogram(position="identity") +  labs(title = "c Repeated Activities",y="# Students-Module pairs",x="# Repeated Activities") + geom_histogram(fill="grey")

psych_quiz <- ggplot(data = dbs[dbs$domain=="psych",], aes(x=quizGrade*100)) + geom_histogram(position="identity") +  labs(title = "g Quiz Grades",y="# Students-Module pairs",x="Quiz Grade") + geom_histogram(fill="grey")

psych_pretest <- ggplot(data = dbs[dbs$domain=="psych",], aes(x=pretestGrade*100)) + geom_histogram(position="identity") +  labs(title = "f Pretest Scores",y="# Students-Module pairs",x="Pretest Score") + geom_histogram(fill="grey")

psych_retention <- ggplot(data = dbs[dbs$domain=="psych",], aes(x=log(retention_interval))) + geom_histogram(position="identity") +  labs(title = "h Retention Interval",y="# Students-Module pairs",x="Log(Retention Interval)") + geom_histogram(fill="grey")

p <- as.data.table(dbs)[domain=="psych",.(nquizzes=length(module)),by=.(ds_anon_user_id,domain)]
psych_numberquizzes <-  ggplot(data = p, aes(x=nquizzes)) + geom_histogram(position="identity") +  labs(title = "e Number of Modules Completed",y="# Students",x="Number of Quizzes") + geom_histogram(fill="grey")

ggarrange(psych_act, psych_pages, psych_rep_act, psych_rep_pages,  psych_numberquizzes,psych_pretest, psych_quiz, psych_retention, common.legend = TRUE, ncol = 2, nrow = 4, legend = "bottom")

```

## Computing
```{r}
computing_pages <- ggplot(data = dbs[dbs$domain=="c@cm",], aes(x=percentPages*100)) + geom_histogram(position="identity") +  labs(title = "b Pages Viewed",y="# Students-Module pairs",x="% Pages") + geom_histogram(fill="grey")

computing_act <- ggplot(data = dbs[dbs$domain=="c@cm",], aes(x=percentActivities*100)) + geom_histogram(position="identity") + labs(title = "a Activities Completed",y="# Students-Module pairs",x="% Activities") + geom_histogram(fill="grey")

computing_rep_pages <- ggplot(data = dbs[dbs$domain=="c@cm",], aes(x=repeated_pages)) + geom_histogram(position="identity") +  labs(title = "d Repeated Pages",y="# Students-Module pairs",x="# Repeated Pages") + geom_histogram(fill="grey")

computing_rep_act <- ggplot(data = dbs[dbs$domain=="c@cm",], aes(x=repeated_activities)) + geom_histogram(position="identity") +  labs(title = "c Repeated Activities",y="# Students-Module pairs",x="# Repeated Activities") + geom_histogram(fill="grey")

computing_quiz <- ggplot(data = dbs[dbs$domain=="c@cm",], aes(x=quizGrade*100)) + geom_histogram(position="identity") +  labs(title = "g Quiz Grades",y="# Students-Module pairs",x="Quiz Grade") + geom_histogram(fill="grey")

computing_pretest <- ggplot(data = dbs[dbs$domain=="c@cm",], aes(x=pretestGrade*100)) + geom_histogram(position="identity") +  labs(title = "f Pretest Scores",y="# Students-Module pairs",x="Pretest Score") + geom_histogram(fill="grey")

computing_retention <- ggplot(data = dbs[dbs$domain=="c@cm",], aes(x=log(retention_interval))) + geom_histogram(position="identity") +  labs(title = "h Retention Interval",y="# Students-Module pairs",x="Log(Retention Interval)") + geom_histogram(fill="grey")

p <- as.data.table(dbs)[domain=="c@cm",.(nquizzes=length(module)),by=.(ds_anon_user_id,domain)]
computing_numberquizzes <-  ggplot(data = p, aes(x=nquizzes)) + geom_histogram(position="identity") +  labs(title = "e Number of Modules Completed",y="# Students",x="Number of Quizzes") + geom_histogram(fill="grey")

ggarrange(computing_act, computing_pages, computing_rep_act, computing_rep_pages,  computing_numberquizzes,computing_pretest, computing_quiz, computing_retention, common.legend = TRUE, ncol = 2, nrow = 4, legend = "bottom")

```

# STUDY 1: PSYCH COURSE

## What is the effect of completing more activities vs. viewing more pages?
```{r}
## plot performance by number of activities completed
dbs_psych <-  dbs[dbs$dataset=="ds863",]
dbs_psych <- mutate(dbs_psych,quantile_naction=ntile(dbs_psych$NAction,10))
dbs_psych <- as.data.table(dbs_psych)

dbs_psych_sum <- dbs_psych[,.(grade=mean(quizGrade),naction_avg=mean(NAction),n=.N),by=.(quantile_naction)]

activities_psych <- ggplot(data=dbs_psych_sum, aes(x=naction_avg, y=grade)) + geom_point(aes(size = n/100)) + theme_classic() + xlab("Number of Activities Completed") + ylab("Quiz Grade") + scale_linetype(name="Retention Interval Quintile") + scale_shape_discrete(name="Retention Interval Quintile") + theme(legend.justification=c(1,0), legend.position="none",plot.title = element_text(hjust = 0.5)) + ggtitle("Practice") + coord_cartesian(ylim=c(0.70,0.95)) + geom_smooth(method = "lm") + scale_size_identity()
activities_psych

## plot performance by % of activities completed

dbs_psych <-  dbs[dbs$dataset=="ds863",]
dbs_psych <- mutate(dbs_psych,quantile_naction=ntile(dbs_psych$percentActivities,10))
dbs_psych <- as.data.table(dbs_psych)

dbs_psych_sum <- dbs_psych[,.(grade=mean(quizGrade),naction_avg=mean(percentActivities)*100,n=.N),by=.(quantile_naction)]

activities_psych <- ggplot(data=dbs_psych_sum, aes(x=naction_avg, y=grade)) + geom_point(aes(size = n/100)) + theme_classic() + xlab("% of Activities Completed") + ylab("Quiz Grade") + scale_linetype(name="Retention Interval Quintile") + scale_shape_discrete(name="Retention Interval Quintile") + theme(legend.justification=c(1,0), legend.position="none",plot.title = element_text(hjust = 0.5)) + ggtitle("Practice") + coord_cartesian(ylim=c(0.70,0.95)) + geom_smooth(method = "lm") + scale_size_identity()
activities_psych

## plot performance by number of pages accessed

dbs_psych <-  dbs[dbs$dataset=="ds863",]
dbs_psych <- mutate(dbs_psych,quantile_nread=ntile(dbs_psych$NRead_trimmed,10))
dbs_psych <- as.data.table(dbs_psych)

dbs_psych_sum <- dbs_psych[,.(grade=mean(quizGrade),nread_avg=mean(NRead_trimmed),n=.N),by=.(quantile_nread)]

library(ggplot2)
read_psych <- ggplot(data=dbs_psych_sum, aes(x=nread_avg, y=grade)) + geom_point(aes(size = n/100)) + theme_classic() + xlab("Number of Pages Viewed") + ylab("Quiz Grade") + scale_linetype(name="Retention Interval Quintile") + scale_shape_discrete(name="Retention Interval Quintile") + theme(legend.justification=c(1,0), legend.position="none",plot.title = element_text(hjust = 0.5)) + ggtitle("Reading") + coord_cartesian(ylim=c(0.70,0.95)) + geom_smooth(method = "lm") + scale_size_identity()
read_psych

## plot performance by % of pages accessed

dbs_psych <-  dbs[dbs$dataset=="ds863",]
dbs_psych <- mutate(dbs_psych,quantile_nread=ntile(dbs_psych$percentPages,20))
dbs_psych <- as.data.table(dbs_psych)

dbs_psych_sum <- dbs_psych[,.(grade=mean(quizGrade),nread_avg=mean(percentPages)*100,n=.N),by=.(quantile_nread)]

library(ggplot2)
read_psych <- ggplot(data=dbs_psych_sum, aes(x=nread_avg, y=grade)) + geom_point(aes(size = n/100)) + theme_classic() + xlab("% of Pages Viewed") + ylab("Quiz Grade") + scale_linetype(name="Retention Interval Quintile") + scale_shape_discrete(name="Retention Interval Quintile") + theme(legend.justification=c(1,0), legend.position="none",plot.title = element_text(hjust = 0.5)) + ggtitle("Reading") + coord_cartesian(ylim=c(0.70,0.95)) + geom_smooth(method = "lm") + scale_size_identity()
read_psych

## Create plot with two panels (Do and Read)
ggarrange(plotlist = list(activities_psych,read_psych),nrow=1,ncol=2)

## Stats model comparing doing vs. no doing and reading vs. no reading
summary(absolute_read <- lmer(zquizGrade ~ zpretestGrade+activity_group+read_group+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",]))

mean(dbs$quizGrade[dbs$activity_group=="2_Activities"&dbs$dataset=="ds863"]); sd(dbs$quizGrade[dbs$activity_group=="2_Activities"&dbs$dataset=="ds863"])

mean(dbs$quizGrade[dbs$activity_group=="1_No Activities"&dbs$dataset=="ds863"]); sd(dbs$quizGrade[dbs$activity_group=="1_No Activities"&dbs$dataset=="ds863"])

mean(dbs$quizGrade[dbs$read_group=="2_Read"&dbs$dataset=="ds863"]); sd(dbs$quizGrade[dbs$read_group=="2_Read"&dbs$dataset=="ds863"])
mean(dbs$quizGrade[dbs$read_group=="1_No Read"&dbs$dataset=="ds863"]); sd(dbs$quizGrade[dbs$read_group=="1_No Read"&dbs$dataset=="ds863"])

## Stats model comparing dosage of doing and dosage of reading (including pretest as main effect and interaction with performance in the module)

### With number of activities/pages
dosage_pretestonly <- lmer(zquizGrade ~ zpretestGrade+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

dosage_actiononly <- lmer(zquizGrade ~ zpretestGrade+zNAction+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

dosage_readonly <- lmer(zquizGrade ~ zpretestGrade+zNRead_trimmed+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

dosage_actionRead <- lmer(zquizGrade ~ zpretestGrade+zNAction+zNRead_trimmed+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

dosage_actionRead_correctness <- lmer(zquizGrade ~ zpretestGrade+zcorrectness_alltries+zNAction+zNRead_trimmed+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

anova(dosage_pretestonly,dosage_actiononly,dosage_readonly,dosage_actionRead,dosage_actionRead_correctness)

anova(dosage_actionRead,dosage_actionRead_correctness)

### With % of activities/pages
dosage_actiononly <- lmer(zquizGrade ~ zpretestGrade+zpercentActivities+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

dosage_readonly <- lmer(zquizGrade ~ zpretestGrade+zpercentPages+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

dosage_actionRead <- lmer(zquizGrade ~ zpretestGrade+zpercentActivities+zpercentPages+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

dosage_actionRead_correctness <- lmer(zquizGrade ~ zpretestGrade+zcorrectness_alltries+zpercentActivities+zpercentPages+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

anova(dosage_pretestonly,dosage_actiononly,dosage_readonly,dosage_actionRead,dosage_actionRead_correctness)

anova(dosage_actionRead,dosage_actionRead_correctness)

summary(dosage_actionRead_correctness)

### With time spent in activities/pages
dosage_actiononly <- lmer(zquizGrade ~ zpretestGrade+logTimeAction+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

dosage_readonly <- lmer(zquizGrade ~ zpretestGrade+logTimeReadTrimmed+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

dosage_actionRead <- lmer(zquizGrade ~ zpretestGrade+logTimeAction+logTimeReadTrimmed+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

dosage_actionRead_correctness <- lmer(zquizGrade ~ zpretestGrade+zcorrectness_alltries+logTimeAction+logTimeReadTrimmed+(1|ds_anon_user_id)+(1|module),data = dbs[dbs$dataset=="ds863",])

#anova(dosage_pretestonly,dosage_actiononly,dosage_readonly,dosage_actionRead,dosage_actionRead_correctness)

anova(dosage_actionRead,dosage_actionRead_correctness)

summary(dosage_actionRead_correctness)
```

## Investigate characteristics of practice: why is it beneficial?
```{r}
## set things up
psych_step <- fread("~/Google Drive/My Drive/Projects/Doer Effect paper analyses/datasets/transaction_logs/psych/ds863/ds863_student_step_All_Data_2287_2019_0803_061943.txt",check.names = TRUE)

library(lubridate)
psych_step$Step.Start.Time <- ymd_hms(psych_step$Step.Start.Time)

psych_step <- setorder(psych_step,"Anon.Student.Id","KC..psychology.1.4.","Step.Start.Time")

psych_step_unique <- psych_step[which(psych_step$Problem.View==1),]
psych_step_repeated <- psych_step[!which(psych_step$Problem.View==1),]

setDT(psych_step_unique)[, UniqueOpp := seq_len(.N)-1, by=rleid(Anon.Student.Id,KC..psychology.1.4.)]
psych_step_unique$Opp <- psych_step_unique$UniqueOpp
psych_step_unique$RepeatOpp <- NA

setDT(psych_step_repeated)[, RepeatOpp := seq_len(.N), by=rleid(Anon.Student.Id,KC..psychology.1.4.,Step.Name)]
psych_step_repeated$Opp <- psych_step_repeated$RepeatOpp
psych_step_repeated$UniqueOpp <- NA
psych_step_repeated$RepeatOpp <- as.numeric(psych_step_repeated$RepeatOpp)

psych_step_fixed <- rbind(psych_step_unique,psych_step_repeated)

psych_step_fixed <- setorder(psych_step_fixed,"Anon.Student.Id","KC..psychology.1.4.","Step.Start.Time")

psych_step_fixed$RepeatOpp <- if_else(condition = psych_step_fixed$UniqueOpp==0,true = 0,false = c(psych_step_fixed$RepeatOpp),missing = psych_step_fixed$RepeatOpp)

library(tidyverse)
psych_step_fixed <- psych_step_fixed %>% tidyr::fill(UniqueOpp)
psych_step_fixed <- psych_step_fixed %>% tidyr::fill(RepeatOpp)
psych_step_fixed$ItemRepeats <- psych_step_fixed$Problem.View-1

psych_step_fixed$correctness <- ifelse(psych_step_fixed$First.Attempt=="correct",1,0)

psych_step_fixed$repetition <- ifelse(psych_step_fixed$RepeatOpp>1,"repeat","unique")

module_info <- fread("OLI_start_attempt_week_mapping.txt",check.names = TRUE)
names(module_info) <- make.names(c("Problem Name","module"))

psych_step_module <- merge(psych_step_fixed,module_info)
psych_step_module <- psych_step_module[-which(psych_step_module$module==100),]
psych_step_module <- psych_step_module[which(psych_step_module$Anon.Student.Id%in%unique(dbs$ds_anon_user_id)),]

sum_kc_doing <- psych_step_module[,.(nKCs=length(unique(KC..psychology.1.4.)),accuracy=mean(correctness),nProblems=length(unique(Problem.Name)),nActivities_unique=length(Row[repetition=="unique"]),nActivities_repeated=length(Row[repetition=="repeat"])),by=.(Anon.Student.Id,module)]

sum_kc_doing <- ddply(.data = sum_kc_doing,.variables = .(module),.fun = mutate,MaxKCs = max(nKCs))

sum_kc_doing$percentKCs <- sum_kc_doing$nKCs/sum_kc_doing$MaxKCs

names(sum_kc_doing)[1] <- "ds_anon_user_id"
dbs_psych_with_kc <- join(dbs_psych,sum_kc_doing)
dbs_psych_with_kc$percentActivities <- ifelse(is.na(dbs_psych_with_kc$percentActivities),0,dbs_psych_with_kc$percentActivities)

dbs_psych_with_kc$nActivities_unique <- ifelse(is.na(dbs_psych_with_kc$nActivities_unique),0,dbs_psych_with_kc$nActivities_unique)

dbs_psych_with_kc$nActivities_repeated <- ifelse(is.na(dbs_psych_with_kc$nActivities_repeated),0,dbs_psych_with_kc$nActivities_repeated)

dbs_psych_with_kc$nKCs <- ifelse(is.na(dbs_psych_with_kc$nKCs),0,dbs_psych_with_kc$nKCs)
dbs_psych_with_kc$percentKCs <- ifelse(is.na(dbs_psych_with_kc$percentKCs),0,dbs_psych_with_kc$percentKCs)

corr.test(dbs_psych_with_kc$percentActivities,dbs_psych_with_kc$percentKCs)

dbs_psych_with_kc <- ddply(.data = dbs_psych_with_kc,.variables = .(module),.fun = ,mutate,zpercentKCs=scale(percentKCs),znActivities_unique=scale(nActivities_unique),znActivities_repeated=scale(nActivities_repeated))
```

### Is the benefit of practice related to greater coverage?
```{r}
# plot
dbs_psych_with_kc <- ddply(.data = dbs_psych_with_kc,.variables = .(module),.fun = mutate,quantile_do=ntile(percentActivities,4),quantile_kc=ntile(percentKCs,4),quantile_read=ntile(percentPages,4))

quantileSum_do <- ddply(.data = dbs_psych_with_kc,.variables = .(quantile_do),.fun = summarize,quizGrade=mean(quizGrade))

quantileSum_kc <- ddply(.data = dbs_psych_with_kc,.variables = .(quantile_kc),.fun = summarize,quizGrade=mean(quizGrade))

quantileSum_do$quantile_do <- quantileSum_do$quantile_do*25
quantileSum_kc$quantile_kc <- quantileSum_kc$quantile_kc*25

do <- ggplot(quantileSum_do, aes(x=quantile_do, y=quizGrade)) + geom_line()+
  geom_point() + labs(title="Quiz performance by doing and coverage", x ="Quintile Activities Completed", y = "Quiz Grade") + theme_bw()
do

kc <- ggplot(quantileSum_kc, aes(x=quantile_kc, y=quizGrade)) + geom_line()+
  geom_point() +labs(title="Quiz performance by doing and coverage", x ="Quintile Topics Covered", y = "Quiz Grade") + theme_bw()
kc
 
# stats
coverage <- lmer(zquizGrade~zpretestGrade+zcorrectness_alltries+zpercentActivities+zpercentKCs+zpercentPages+(1|ds_anon_user_id)+(1|module),data=dbs_psych_with_kc)

coverage_simplified <- lmer(zquizGrade~zpretestGrade+zpercentActivities+zpercentKCs+zpercentPages+(1|ds_anon_user_id)+(1|module),data=dbs_psych_with_kc)

anova(coverage_simplified,coverage)

summary(coverage)
```

### Is the benefit of practice related to more repetition of the same activities?
```{r}
# plot
dbs_psych_with_kc <- ddply(.data = dbs_psych_with_kc,.variables = .(module),.fun = mutate,quantile_unique=ntile(nActivities_unique,4),quantile_repeated=ntile(nActivities_repeated,4))

quantileSum <- ddply(.data = dbs_psych_with_kc,.variables = .(quantile_unique),.fun = summarize,quizGrade=mean(quizGrade))

quantileSum$quantile_unique <- quantileSum$quantile_unique*25

ggplot(quantileSum, aes(x=quantile_unique, y=quizGrade)) +
  geom_line()+
  geom_point()

quantileSum <- ddply(.data = dbs_psych_with_kc,.variables = .(quantile_repeated),.fun = summarize,quizGrade=mean(quizGrade))

quantileSum$quantile_repeated <- quantileSum$quantile_repeated*25

ggplot(quantileSum, aes(x=quantile_repeated, y=quizGrade)) +
  geom_line()+
  geom_point()

quantileSum <- ddply(.data = dbs_psych_with_kc,.variables = .(quantile_repeated,quantile_unique),.fun = summarize,quizGrade=mean(quizGrade))

quantileSum$quantile_repeated <- quantileSum$quantile_repeated*25
quantileSum$quantile_unique <- quantileSum$quantile_unique*25
quantileSum$quantile_repeated <- as.factor(quantileSum$quantile_repeated)

ggplot(quantileSum, aes(x=quantile_unique, y=quizGrade, group=quantile_repeated)) +
  geom_line(aes(color=quantile_repeated))+
  geom_point(aes(color=quantile_repeated)) + guides(colour=guide_legend(title="Quintile Repetition")) +labs(title="Quiz performance by repeated and unique activities",
        x ="Quintile Unique Activities", y = "Quiz Grade") + theme_bw()

# stats
repetition_simplified <- lmer(zquizGrade~zpretestGrade+znActivities_unique*znActivities_repeated+zpercentKCs+zpercentPages+(1|ds_anon_user_id)+(1|module),data=dbs_psych_with_kc)

repetition <- lmer(zquizGrade~zpretestGrade+zcorrectness_alltries+znActivities_unique*znActivities_repeated+zpercentKCs+zpercentPages+(1|ds_anon_user_id)+(1|module),data=dbs_psych_with_kc)

anova(repetition_simplified,repetition)
summary(repetition)
```

# STUDY 2: COMPUTING

## What is the effect of completing more activities vs. viewing more pages?
```{r}
## plot performance by number of activities completed
dbs_computing <-  dbs[!dbs$dataset=="ds863",]
dbs_computing <- mutate(dbs_computing,quantile_naction=ntile(dbs_computing$NAction,10))
dbs_computing <- as.data.table(dbs_computing)

dbs_computing_sum <- dbs_computing[,.(grade=mean(quizGrade),naction_avg=mean(NAction),n=.N),by=.(quantile_naction)]

activities_computing <- ggplot(data=dbs_computing_sum, aes(x=naction_avg, y=grade)) + geom_point(aes(size = n/25)) + theme_classic() + xlab("Number of Activities Completed") + ylab("Quiz Grade") + scale_linetype(name="Retention Interval Quintile") + scale_shape_discrete(name="Retention Interval Quintile") + theme(legend.justification=c(1,0), legend.position="none",plot.title = element_text(hjust = 0.5)) + ggtitle("Practice") + coord_cartesian(ylim=c(0.70,0.95)) + geom_smooth(method = "lm") + scale_size_identity()
activities_psych

## plot performance by % of activities completed
dbs_computing <-  dbs[!dbs$dataset=="ds863",]
dbs_computing <- mutate(dbs_computing,quantile_naction=ntile(dbs_computing$percentActivities,10))
dbs_computing <- as.data.table(dbs_computing)

dbs_computing_sum <- dbs_computing[,.(grade=mean(quizGrade),naction_avg=mean(percentActivities)*100,n=.N),by=.(quantile_naction)]

activities_computing <- ggplot(data=dbs_computing_sum, aes(x=naction_avg, y=grade)) + geom_point(aes(size = n/25)) + theme_classic() + xlab("% Activities Completed") + ylab("Quiz Grade") + scale_linetype(name="Retention Interval Quintile") + scale_shape_discrete(name="Retention Interval Quintile") + theme(legend.justification=c(1,0), legend.position="none",plot.title = element_text(hjust = 0.5)) + ggtitle("Practice") + coord_cartesian(ylim=c(0.70,0.95)) + geom_smooth(method = "lm") + scale_size_identity()
activities_computing

## plot performance by number of pages accessed

dbs_computing <-  dbs[!dbs$dataset=="ds863",]
dbs_computing <- mutate(dbs_computing,quantile_nread=ntile(dbs_computing$NRead_trimmed,10))
dbs_computing <- as.data.table(dbs_computing)

dbs_computing_sum <- dbs_computing[,.(grade=mean(quizGrade),nread_avg=mean(NRead_trimmed),n=.N),by=.(quantile_nread)]

library(ggplot2)
read_computing <- ggplot(data=dbs_computing_sum, aes(x=nread_avg, y=grade)) + geom_point(aes(size = n/25)) + theme_classic() + xlab("Number of Pages Viewed") + ylab("Quiz Grade") + scale_linetype(name="Retention Interval Quintile") + scale_shape_discrete(name="Retention Interval Quintile") + theme(legend.justification=c(1,0), legend.position="none",plot.title = element_text(hjust = 0.5)) + ggtitle("Reading") + coord_cartesian(ylim=c(0.70,0.95)) + geom_smooth(method = "lm") + scale_size_identity()
read_computing

## plot performance by % of pages accessed
dbs_computing <-  dbs[!dbs$dataset=="ds863",]
dbs_computing <- mutate(dbs_computing,quantile_nread=ntile(dbs_computing$percentPages,10))
dbs_computing <- as.data.table(dbs_computing)

dbs_computing_sum <- dbs_computing[,.(grade=mean(quizGrade),nread_avg=mean(percentPages)*100,n=.N),by=.(quantile_nread)]

library(ggplot2)
read_computing <- ggplot(data=dbs_computing_sum, aes(x=nread_avg, y=grade)) + geom_point(aes(size = n/25)) + theme_classic() + xlab("% Pages Viewed") + ylab("Quiz Grade") + scale_linetype(name="Retention Interval Quintile") + scale_shape_discrete(name="Retention Interval Quintile") + theme(legend.justification=c(1,0), legend.position="none",plot.title = element_text(hjust = 0.5)) + ggtitle("Reading") + coord_cartesian(ylim=c(0.70,0.95)) + geom_smooth(method = "lm") + scale_size_identity()
read_computing

## Create plot with two panels (Do and Read)
ggarrange(plotlist = list(activities_computing,read_computing),nrow=1,ncol=2)

# Stats model comparing doing vs. no doing and reading vs. no reading
summary(absolute_read <- lmer(zquizGrade ~ zpretestGrade+activity_group+read_group+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",]))


mean(dbs$quizGrade[dbs$activity_group=="2_Activities"&!dbs$dataset=="ds863"]); sd(dbs$quizGrade[dbs$activity_group=="2_Activities"&!dbs$dataset=="ds863"])

mean(dbs$quizGrade[dbs$activity_group=="1_No Activities"&!dbs$dataset=="ds863"]); sd(dbs$quizGrade[dbs$activity_group=="1_No Activities"&!dbs$dataset=="ds863"])

mean(dbs$quizGrade[dbs$read_group=="2_Read"&!dbs$dataset=="ds863"]); sd(dbs$quizGrade[dbs$read_group=="2_Read"&!dbs$dataset=="ds863"])

mean(dbs$quizGrade[dbs$read_group=="1_No Read"&!dbs$dataset=="ds863"]); sd(dbs$quizGrade[dbs$read_group=="1_No Read"&!dbs$dataset=="ds863"])

## Stats model comparing dosage of doing and dosage of reading (including pretest as main effect and interaction with performance in the module)

### With number of activities/pages
summary(dosage <- lmer(zquizGrade ~ zpretestGrade+zcorrectness_alltries+zNAction+zNRead_trimmed+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",]))

### With % of activities/pages
summary(dosage <- lmer(zquizGrade ~ zpretestGrade+zcorrectness_alltries+zpercentActivities+zpercentPages+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",]))

### With time spent in activities/pages
summary(dosage <- lmer(zquizGrade ~ zpretestGrade+zcorrectness_alltries+logtime_perDo+logtime_perPage+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",]))

## Stats model comparing dosage of doing and dosage of reading (including pretest as main effect and interaction with performance in the module AND pretest)

### With number of activities/pages
dosage_pretestonly <- lmer(zquizGrade ~ zpretestGrade+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",])

dosage_actiononly <- lmer(zquizGrade ~ zpretestGrade+zNAction+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",])

dosage_readonly <- lmer(zquizGrade ~ zpretestGrade+zNRead_trimmed+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",])

dosage_actionRead <- lmer(zquizGrade ~ zpretestGrade+zNAction+zNRead_trimmed+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",])

dosage_actionRead_correctness <- lmer(zquizGrade ~ zpretestGrade+zcorrectness_alltries+zNAction+zNRead_trimmed+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",])

anova(dosage_pretestonly,dosage_actiononly,dosage_readonly,dosage_actionRead,dosage_actionRead_correctness)

anova(dosage_actionRead,dosage_actionRead_correctness)
summary(dosage_actionRead_correctness)

### With % of activities/pages
dosage_actiononly <- lmer(zquizGrade ~ zpretestGrade+zpercentActivities+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",])

dosage_readonly <- lmer(zquizGrade ~ zpretestGrade+zpercentPages+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",])

dosage_actionRead <- lmer(zquizGrade ~ zpretestGrade+zpercentActivities+zpercentPages+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",])

dosage_actionRead_correctness <- lmer(zquizGrade ~ zpretestGrade+zcorrectness_alltries+zpercentActivities+zpercentPages+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",])

anova(dosage_pretestonly,dosage_actiononly,dosage_readonly,dosage_actionRead,dosage_actionRead_correctness)

anova(dosage_actionRead,dosage_actionRead_correctness)
summary(dosage_actionRead_correctness)

### With time spent in activities/pages
summary(dosage <- lmer(zquizGrade ~ zpretestGrade+zcorrectness_alltries+logtime_perPage+logtime_perDo+(1|ds_anon_user_id)+(1|module),data = dbs[!dbs$dataset=="ds863",]))
```
## Investigate characteristics of practice: why is it beneficial?
```{r}
## set things up
#load transaction info

c_cm_step <- fread("ds2033_student_step_All_Data_3802_2017_0319_041932_multiskill_converted.txt",check.names = TRUE)
c_cm_step$dataset <- "ds2033"
c_cm_step2 <- fread("ds490_student_step_All_Data_1586_2020_1118_065941.txt",check.names = TRUE)
c_cm_step2$dataset <- "ds490"

#c_cm_step <- fread("ds2033_student_step_no_post_6636_2020_1012_161834_multiskill_converted.txt",check.names = TRUE)
c_cm_step <- rbind(c_cm_step,c_cm_step2[,c(1:22,29)])

c_cm_step

#c_cm_step <- c_cm_step[-which(c_cm_step$Problem.Name=="ccm_final_exam"),]

library(lubridate)
c_cm_step$Step.Start.Time <- ymd_hms(c_cm_step$Step.Start.Time)

c_cm_step <- setorder(c_cm_step,"Anon.Student.Id","KC..LOv1.PVfixed.models.","Step.Start.Time")

c_cm_step_unique <- c_cm_step[which(c_cm_step$Problem.View==1),]
c_cm_step_repeated <- c_cm_step[!which(c_cm_step$Problem.View==1),]

### add an item counter ###

setDT(c_cm_step_unique)[, UniqueOpp := seq_len(.N)-1, by=rleid(Anon.Student.Id,KC..LOv1.PVfixed.models.)]
c_cm_step_unique$Opp <- c_cm_step_unique$UniqueOpp
c_cm_step_unique$RepeatOpp <- NA

setDT(c_cm_step_repeated)[, RepeatOpp := seq_len(.N), by=rleid(Anon.Student.Id,KC..LOv1.PVfixed.models.,Step.Name)]
c_cm_step_repeated$Opp <- c_cm_step_repeated$RepeatOpp
c_cm_step_repeated$UniqueOpp <- NA
c_cm_step_repeated$RepeatOpp <- as.numeric(c_cm_step_repeated$RepeatOpp)

c_cm_step_fixed <- rbind(c_cm_step_unique,c_cm_step_repeated)

c_cm_step_fixed <- setorder(c_cm_step_fixed,"Anon.Student.Id","KC..LOv1.PVfixed.models.","Step.Start.Time")

c_cm_step_fixed$RepeatOpp <- if_else(condition = c_cm_step_fixed$UniqueOpp==0,true = 0,false = c(c_cm_step_fixed$RepeatOpp),missing = c_cm_step_fixed$RepeatOpp)

library(tidyverse)
c_cm_step_fixed <- c_cm_step_fixed %>% tidyr::fill(UniqueOpp)
c_cm_step_fixed <- c_cm_step_fixed %>% tidyr::fill(RepeatOpp)
c_cm_step_fixed$ItemRepeats <- c_cm_step_fixed$Problem.View-1

c_cm_step_fixed$correctness <- ifelse(c_cm_step_fixed$First.Attempt=="correct",1,0)


c_cm_step_fixed$repetition <- ifelse(c_cm_step_fixed$RepeatOpp>1,"repeat","unique")

quizDatesTable_ds2033 <- fread("ds2033_quizDatesTable.csv",check.names = TRUE)
names(quizDatesTable_ds2033)[1] <-  "Anon.Student.Id"

quizDatesTable_ds490 <- fread("ds490_quizDatesTable.csv",check.names = TRUE)
names(quizDatesTable_ds490)[1] <-  "Anon.Student.Id"

quizDatesTable <- rbind(quizDatesTable_ds2033,quizDatesTable_ds490)

quizDatesTable$pt1 <- ymd_hms(quizDatesTable$pt1)
quizDatesTable$pt2 <- ymd_hms(quizDatesTable$pt2)
quizDatesTable$pt3 <- ymd_hms(quizDatesTable$pt3)
quizDatesTable$pt4 <- ymd_hms(quizDatesTable$pt4)
quizDatesTable$quiz1 <- ymd_hms(quizDatesTable$quiz1)
quizDatesTable$quiz2 <- ymd_hms(quizDatesTable$quiz2)
quizDatesTable$quiz3 <- ymd_hms(quizDatesTable$quiz3)
quizDatesTable$quiz4 <- ymd_hms(quizDatesTable$quiz4)
quizDatesTable$exam <- ymd_hms(quizDatesTable$exam)

c_cm_step_module <- join(c_cm_step_fixed,quizDatesTable)

c_cm_step_module$module <- ifelse(c_cm_step_module$Step.Start.Time>c_cm_step_module$pt1&c_cm_step_module$Step.Start.Time<c_cm_step_module$quiz1,1,ifelse(c_cm_step_module$Step.Start.Time>c_cm_step_module$pt2&c_cm_step_module$Step.Start.Time<c_cm_step_module$quiz2,2,ifelse(c_cm_step_module$Step.Start.Time>c_cm_step_module$pt3&c_cm_step_module$Step.Start.Time<c_cm_step_module$quiz3,3,ifelse(c_cm_step_module$Step.Start.Time>c_cm_step_module$pt4&c_cm_step_module$Step.Start.Time<c_cm_step_module$quiz4,4,NA))))

c_cm_step_module <- c_cm_step_module[which(c_cm_step_module$Anon.Student.Id%in%unique(dbs$ds_anon_user_id)),]

c_cm_step_module <- c_cm_step_module[-which(is.na(c_cm_step_module$module)),]

sum_kc_doing <- c_cm_step_module[,.(nKCs=length(unique(KC..LOv1.PVfixed.models.)),accuracy=mean(correctness),nProblems=length(unique(Problem.Name)),nActivities_unique=length(Row[repetition=="unique"]),nActivities_repeated=length(Row[repetition=="repeat"])),by=.(Anon.Student.Id,module)]

sum_kc_doing <- ddply(.data = sum_kc_doing,.variables = .(module),.fun = mutate,MaxKCs = max(nKCs))

sum_kc_doing$percentKCs <- sum_kc_doing$nKCs/sum_kc_doing$MaxKCs

names(sum_kc_doing)[1] <- "ds_anon_user_id"
dbs_computing_with_kc <- join(dbs_computing,sum_kc_doing) 

dbs_computing_with_kc$percentActivities <- ifelse(is.na(dbs_computing_with_kc$percentActivities),0,dbs_computing_with_kc$percentActivities)

dbs_computing_with_kc$nActivities_unique <- ifelse(is.na(dbs_computing_with_kc$nActivities_unique),0,dbs_computing_with_kc$nActivities_unique)

dbs_computing_with_kc$nActivities_repeated <- ifelse(is.na(dbs_computing_with_kc$nActivities_repeated),0,dbs_computing_with_kc$nActivities_repeated)

dbs_computing_with_kc$nKCs <- ifelse(is.na(dbs_computing_with_kc$nKCs),0,dbs_computing_with_kc$nKCs)

dbs_computing_with_kc$percentKCs <- ifelse(is.na(dbs_computing_with_kc$percentKCs),0,dbs_computing_with_kc$percentKCs)

corr.test(dbs_computing_with_kc$percentActivities,dbs_computing_with_kc$percentKCs)

dbs_computing_with_kc <- ddply(.data = dbs_computing_with_kc,.variables = .(module),.fun = ,mutate,zpercentKCs=scale(percentKCs),znActivities_unique=scale(nActivities_unique),znActivities_repeated=scale(nActivities_repeated))
```


### Is the benefit of practice related to more repetition of the same activities?
```{r}
## analyses as for Study 1
#plot
dbs_computing_with_kc <- ddply(.data = dbs_computing_with_kc,.variables = .(module),.fun = mutate,quantile_unique=ntile(nActivities_unique,4),quantile_repeated=ntile(nActivities_repeated,4))

quantileSum <- ddply(.data = dbs_computing_with_kc,.variables = .(quantile_unique),.fun = summarize,quizGrade=mean(quizGrade))

quantileSum$quantile_unique <- quantileSum$quantile_unique*25

ggplot(quantileSum, aes(x=quantile_unique, y=quizGrade)) +
  geom_line()+
  geom_point()

quantileSum <- ddply(.data = dbs_computing_with_kc,.variables = .(quantile_repeated),.fun = summarize,quizGrade=mean(quizGrade))

quantileSum$quantile_repeated <- quantileSum$quantile_repeated*25

ggplot(quantileSum, aes(x=quantile_repeated, y=quizGrade)) +
  geom_line()+
  geom_point()

quantileSum <- ddply(.data = dbs_computing_with_kc,.variables = .(quantile_repeated,quantile_unique),.fun = summarize,quizGrade=mean(quizGrade))

quantileSum$quantile_repeated <- quantileSum$quantile_repeated*25
quantileSum$quantile_unique <- quantileSum$quantile_unique*25
quantileSum$quantile_repeated <- as.factor(quantileSum$quantile_repeated)

ggplot(quantileSum, aes(x=quantile_unique, y=quizGrade, group=quantile_repeated)) +
  geom_line(aes(color=quantile_repeated))+
  geom_point(aes(color=quantile_repeated)) + guides(colour=guide_legend(title="Quintile Repetition")) +labs(title="Quiz performance by repeated and unique activities",
        x ="Quintile Unique Activities", y = "Quiz Grade") + theme_bw()

# stats
repetition_simplified <- lmer(zquizGrade~zpretestGrade+znActivities_unique*znActivities_repeated+zpercentKCs+zpercentPages+(1|ds_anon_user_id),data=dbs_computing_with_kc)

repetition <- lmer(zquizGrade~zpretestGrade+zcorrectness_alltries+znActivities_unique*znActivities_repeated+zpercentKCs+zpercentPages+(1|ds_anon_user_id),data=dbs_computing_with_kc)

anova(repetition_simplified,repetition)

summary(repetition)

## Same analysis as above but at the KC level
#get quiz data for each KC
quizPerformanceData <- c_cm_step_fixed[Problem.Name%in%c("_u01_m01_metacog_quiz","_u02_exam_ready_quiz","_u03_exam_ready_quiz","_u04_exam_ready_quiz","_u05_exam_ready_quiz"),.(quizGrade=mean(correctness)),by=.(Anon.Student.Id,KC..LOv1.PVfixed.models.)]

#quizPerformanceData <- ddply(.data = c_cm_step_fixed[c_cm_step_fixed$Problem.Name%in%c("_u01_m01_metacog_quiz","_u02_exam_ready_quiz","_u03_exam_ready_quiz","_u04_exam_ready_quiz","_u05_exam_ready_quiz"),],.variables = .(Anon.Student.Id,KC..LOv1.PVfixed.models.),.fun = summarize,quizGrade=mean(correctness))

pretestPerformanceData <- c_cm_step_fixed[Problem.Name%in%c("_u02_m0_self_eval_a2-pt1","_u02_m0_self_eval_a2-pt3","_u02_m0_self_eval_a2-pt2","_u03_m0_self_eval_a2-pt1","_u03_m0_self_eval_a2-pt2","_u03_m0_self_eval_a2-pt3","_u04_m0_self_eval_a2-pt1","_u04_m0_self_eval_a2-pt2","_u04_m0_self_eval_a2-pt3","_u05_m0_self_eval_a2-pt1","_u05_m0_self_eval_a2-pt2","_u05_m0_self_eval_a2-pt3"),.(pretestGrade=mean(correctness)),by=.(Anon.Student.Id,KC..LOv1.PVfixed.models.)]

#pretestPerformanceData <- ddply(.data = c_cm_step_fixed[c_cm_step_fixed$Problem.Name%in%c("_u02_m0_self_eval_a2-pt1","_u02_m0_self_eval_a2-pt3","_u02_m0_self_eval_a2-pt2","_u03_m0_self_eval_a2-pt1","_u03_m0_self_eval_a2-pt2","_u03_m0_self_eval_a2-pt3","_u04_m0_self_eval_a2-pt1","_u04_m0_self_eval_a2-pt2","_u04_m0_self_eval_a2-pt3","_u05_m0_self_eval_a2-pt1","_u05_m0_self_eval_a2-pt2","_u05_m0_self_eval_a2-pt3"),],.variables = .(Anon.Student.Id,KC..LOv1.PVfixed.models.),.fun = summarize,pretestGrade=mean(correctness))

PerformanceData <- c_cm_step_fixed[!Problem.Name%in%c("_u02_m0_self_eval_a2-pt1","_u02_m0_self_eval_a2-pt3","_u02_m0_self_eval_a2-pt2","_u03_m0_self_eval_a2-pt1","_u03_m0_self_eval_a2-pt2","_u03_m0_self_eval_a2-pt3","_u04_m0_self_eval_a2-pt1","_u04_m0_self_eval_a2-pt2","_u04_m0_self_eval_a2-pt3","_u05_m0_self_eval_a2-pt1","_u05_m0_self_eval_a2-pt2","_u05_m0_self_eval_a2-pt3","_u01_m01_metacog_quiz","_u02_exam_ready_quiz","_u03_exam_ready_quiz","_u04_exam_ready_quiz","_u05_exam_ready_quiz"),.(activity_performance=mean(correctness)),by=.(Anon.Student.Id,KC..LOv1.PVfixed.models.)]

examData <- c_cm_step_fixed[Problem.Name%in%c("ccm_final_exam"),.(ExamGrade=mean(correctness)),by=.(Anon.Student.Id,KC..LOv1.PVfixed.models.)]

#examData <- ddply(.data = c_cm_step_fixed[c_cm_step_fixed$Problem.Name%in%c("ccm_final_exam"),],.variables = .(Anon.Student.Id,KC..LOv1.PVfixed.models.),.fun = summarize,ExamGrade=mean(correctness))

activityData <- c_cm_step_module[!c_cm_step_module$Problem.Name%in%c("_u02_m0_self_eval_a2-pt1","_u02_m0_self_eval_a2-pt3","_u02_m0_self_eval_a2-pt2","_u03_m0_self_eval_a2-pt1","_u03_m0_self_eval_a2-pt2","_u03_m0_self_eval_a2-pt3","_u04_m0_self_eval_a2-pt1","_u04_m0_self_eval_a2-pt2","_u04_m0_self_eval_a2-pt3","_u05_m0_self_eval_a2-pt1","_u05_m0_self_eval_a2-pt2","_u05_m0_self_eval_a2-pt3","ccm_final_exam","_u01_m01_metacog_quiz","_u02_exam_ready_quiz","_u03_exam_ready_quiz","_u04_exam_ready_quiz","_u05_exam_ready_quiz"),.(nActivities_unique=length(Row[repetition=="unique"]),nActivities_repeated=length(Row[repetition=="repeat"]),activity_performance=mean(correctness)),by=.(Anon.Student.Id,KC..LOv1.PVfixed.models.)]

#activityData <- ddply(.data = c_cm_step_module[!c_cm_step_module$Problem.Name%in%c("_u02_m0_self_eval_a2-pt1","_u02_m0_self_eval_a2-pt3","_u02_m0_self_eval_a2-pt2","_u03_m0_self_eval_a2-pt1","_u03_m0_self_eval_a2-pt2","_u03_m0_self_eval_a2-pt3","_u04_m0_self_eval_a2-pt1","_u04_m0_self_eval_a2-pt2","_u04_m0_self_eval_a2-pt3","_u05_m0_self_eval_a2-pt1","_u05_m0_self_eval_a2-pt2","_u05_m0_self_eval_a2-pt3","ccm_final_exam","_u01_m01_metacog_quiz","_u02_exam_ready_quiz","_u03_exam_ready_quiz","_u04_exam_ready_quiz","_u05_exam_ready_quiz"),],.variables = .(Anon.Student.Id,KC..LOv1.PVfixed.models.),.fun = summarize,nActivities_unique=length(Row[repetition=="unique"]),nActivities_repeated=length(Row[repetition=="repeat"]))

dbs_c_cm_kc_level <- join(quizPerformanceData,pretestPerformanceData)
dbs_c_cm_kc_level <- join(dbs_c_cm_kc_level,activityData)
dbs_c_cm_kc_level <- join(dbs_c_cm_kc_level,examData)

dbs_c_cm_kc_level <- dbs_c_cm_kc_level[dbs_c_cm_kc_level$Anon.Student.Id%in%dbs_computing_with_kc$ds_anon_user_id,]

dbs_c_cm_kc_level <- dbs_c_cm_kc_level[complete.cases(dbs_c_cm_kc_level),]

# plot
dbs_c_cm_kc_level <- ddply(.data = dbs_c_cm_kc_level,.variables = .(KC..LOv1.PVfixed.models.),.fun = mutate,quantile_unique=ntile(nActivities_unique,4),quantile_repeated=ntile(nActivities_repeated,4))

quantileSum <- ddply(.data = dbs_c_cm_kc_level,.variables = .(quantile_repeated,quantile_unique),.fun = summarize,quizGrade=mean(quizGrade))

quantileSum$quantile_repeated <- quantileSum$quantile_repeated*25
quantileSum$quantile_unique <- quantileSum$quantile_unique*25
quantileSum$quantile_repeated <- as.factor(quantileSum$quantile_repeated)

ggplot(quantileSum[!is.na(quantileSum$quantile_unique),], aes(x=quantile_unique, y=quizGrade, group=quantile_repeated)) +
  geom_line(aes(color=quantile_repeated))+
  geom_point(aes(color=quantile_repeated)) + guides(colour=guide_legend(title="Quintile Repetition")) +labs(title="Quiz performance by repeated and unique activities",
        x ="Quintile Unique Activities", y = "Quiz Grade") + theme_bw()

# stats
repetition_simplified <- lmer(scale(quizGrade)~scale(pretestGrade)+scale(nActivities_unique)*scale(nActivities_repeated)+(1|Anon.Student.Id)+(1|KC..LOv1.PVfixed.models.),data=dbs_c_cm_kc_level)

repetition <- lmer(scale(quizGrade)~scale(pretestGrade)+scale(activity_performance)+scale(nActivities_unique)*scale(nActivities_repeated)+(1|Anon.Student.Id)+(1|KC..LOv1.PVfixed.models.),data=dbs_c_cm_kc_level)

anova(repetition_simplified,repetition)
summary(repetition)


###

```

# TABLES
## Psych
```{r}
dbs_psych_with_kc <- as.data.table(dbs_psych_with_kc)

Psych_N_module <- dbs_psych_with_kc[,.(Nstudents =length(unique(ds_anon_user_id)),Nstudents_activity=length(unique(ds_anon_user_id[NAction>0])),Nstudents_pages=length(unique(ds_anon_user_id[NRead_trimmed>0])),nstudents_pages_activities=length(unique(ds_anon_user_id[NRead_trimmed>0&NAction>0])),Nstudents_rep_act=length(unique(ds_anon_user_id[repeated_activities>0])),Nstudents_rep_pages=length(unique(ds_anon_user_id[repeated_pages>0]))),by=.(module)]
Psych_N_module

n_modules_student <- dbs_psych_with_kc[,.(nmodules=length(unique(module)),activities=mean(NAction),pages=mean(NRead_trimmed),repeated=mean(repeated_activities),act_avail=mean(available_activities),available_pages=mean(available_pages)),by=.(ds_anon_user_id)]

n_modules <- n_modules_student[,.(N=.N,activities=mean(activities),pages=mean(pages),repeated=mean(repeated),act_avail=mean(act_avail),available_pages=mean(available_pages)),by=.(nmodules)]

Psych_usage_averages <- dbs_psych_with_kc[,.(activities =mean(NAction),repeated_activities=mean(repeated_activities),pages=mean(NRead_trimmed),reapted_pages=mean(repeated_pages),mean_kcs=mean(nKCs),pretest=mean(pretestGrade),quiz=mean(quizGrade)),by=.(module)]
Psych_usage_averages

Psych_available <- dbs_psych_with_kc[,.(activities =mean(available_activities),pages=mean(available_pages),kcs=mean(MaxKCs,na.rm=T)),by=.(module)]

Psych_available

p<-ggplot(data=Psych_available, aes(x=module, y=activities)) +
  geom_bar(stat="identity") +labs(title="Number of Available Activities", x ="Module", y = "# Activities") + theme_bw()
p
```

## Computing
```{r}
dbs_computing_with_kc <- as.data.table(dbs_computing_with_kc)

computing_N_module <- dbs_computing_with_kc[,.(Nstudents =length(unique(ds_anon_user_id)),Nstudents_activity=length(unique(ds_anon_user_id[NAction>0])),Nstudents_pages=length(unique(ds_anon_user_id[NRead_trimmed>0])),nstudents_pages_activities=length(unique(ds_anon_user_id[NRead_trimmed>0&NAction>0])),Nstudents_rep_act=length(unique(ds_anon_user_id[repeated_activities>0])),Nstudents_rep_pages=length(unique(ds_anon_user_id[repeated_pages>0]))),by=.(module)]
computing_N_module

computing_usage_averages <- dbs_computing_with_kc[,.(activities =mean(NAction),repeated_activities=mean(repeated_activities),pages=mean(NRead_trimmed),reapted_pages=mean(repeated_pages),mean_kcs=mean(nKCs),pretest=mean(pretestGrade),quiz=mean(quizGrade)),by=.(module)]
computing_usage_averages

computing_available <- dbs_computing_with_kc[,.(activities =mean(available_activities),pages=mean(available_pages),kcs=mean(MaxKCs,na.rm=T)),by=.(module)]
computing_available
```